---
title: "week3_433"
author: "Duohan Zhang"
date: "9/28/2021"
output: github_document
---

## github: https://github.com/duohan0520/stat_433_week3

```{r}
library(nycflights13)
library(tidyverse)
```

1. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
sum( is.na(flights["dep_time"]))
```

```{r}
sum( is.na(flights["arr_delay"]))
sum( is.na(flights["tailnum"]))
sum( is.na(flights["air_time"]))
```

Other variables including arr_delay, tail_num and air_time have missing values. For missing dep_time, they may represent canceled flights. For missing arr_delay and air_time, they may represent canceled flights and departured flights that are unable to complete the flights. 




2. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
flights_new = mutate(flights, dep_time_in_min = dep_time %/% 100 * 60 + dep_time %% 100, 
                     sched_dep_time_in_min = sched_dep_time %/% 100 * 60 + sched_dep_time %%100)
head(flights_new[c("dep_time","sched_dep_time","dep_time_in_min","sched_dep_time_in_min")])
```


3. Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()
```{r}
xx = flights %>%
  group_by(year, month, day) %>%
  summarise( num_canceled_flights = sum(is.na(arr_time)), pro_delay = sum(arr_delay >0,na.rm=T)/n())
ggplot(data= xx,aes(x= num_canceled_flights ,y=pro_delay)) + geom_point()
```
From the picture above, we find that the more pro_delay, the more num_canceled_flights. 



